State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2015-01-22 paper/chapters/4_classification.tex
Paper: Features

\subsection{Features}
As twitter messages are composed of an arbitrary number of words makes it necessary to extract exactly those words which preferably describes the characteristics of such tweets. Extracting those words to an object by making use of various word selecting techniques is called a feature vector. These word selecting techniques are a fundamental process for providing informations to the classification methods, thus an extensive body of different word selecting algorithms exists. 
	\emph{Term Presence} is a method where the feature vector consists of a binary value, $0$ for "term is not present" and $1$ for "term is present". A similar approach is to count the number of occurred words in a message and use the numeric value as a feature, which is called \emph{Term Frequency} but Pang et al. showed \autocite{Pang2008} that Term Presence performed better compared to Term Frequency.
TODO

>>>>

\subsection{Features}
As twitter messages are composed of an arbitrary number of words makes it necessary to extract exactly those words which preferably describes the characteristics of such tweets. Extracting those words to an object by making use of various word selecting techniques is called a feature vector. These word selecting techniques are a fundamental process for providing informations to the classification methods, thus an extensive body of different word selecting algorithms exist. 
	\emph{Term Presence} is a method where the feature vector consists of a binary value, $0$ for "term is not present" and $1$ for "term is present". A similar approach is to count the number of occurred words in a message and use the numeric value as a feature, which is called \emph{Term Frequency} but Pang et al. showed \autocite{Pang2008} that Term Presence performed better compared to Term Frequency.
TODO
